\section*{Notes}

\subsection*{Articles}
\begin{itemize}
    \item From Rasmus: \href{https://github.blog/2024-01-03-our-move-to-generated-sdks/}{Our move to generated SDKs}
\end{itemize}

\subsection*{Thoughts}
\begin{itemize}
    \item \textbf{Default project}: The SDK should be generated on top of a default project, where all the required files are.
    For Java, this could be a Java 8 maven project, with e.g. JetBrains nullable annotations
    For Typescript, this could be an NPM module, with some basic things installed.
    Access Modifier, Type, Name, Value 

    \item \textbf{Variable declarations patterns} Different languages declare variables differently.
    Java, C\#, Python, TypeScript, Go, Rust
    \hyperlink{https://blogger.googleusercontent.com/img/b/R29vZ2xl/AVvXsEjuc3AMG0GuHzqNIR1eLR4h5hTY-DJBgT9LCXziFdJMHiQzRC8L5_5zBrTUuujObkfBtcfyA8XmqK7JbY-vGf-i2M4Fx2Nn8nT6I_9rw0Qg-hw3T40Ha40qjA82Aqs8TLLz1Z5XEJdXE6rpWLQnMc3agYGDKRKda4C5yQnVUQKTWIlyz76rizvgJXNH/s608/2022-12-04_110650.png}{Definations}
    
    \item \textbf{Naming conventions} camelCase, PascalCase, snake\_case, kebab-case \\

    \[Name(carnonical: "IoStream")\]

    \item \textbf{Variable declerations}
    
    \item \textbf{Version Control} An option to export the SDK and give it an id. When a new change is published, it will check if there is any changes from the current SDK.
    Furthermore, an option to detect if the change was a breaking change, e.g. changing a route, removing an element from the body, changing a route signature
    
    \item \textbf{OpenApi} Check if the code should look thru the code, or take input from OpenAPI (or similar) and generate from that.
    Note. Does not support generics, inheritence or polymopishm. \href{https://document360.com/blog/open-api/}{Source}
    
    \item \textbf{Type Serilizer} It should be possible to create a custom sterilizer for each type.
    The sterilizer should have different options, such as required imports (which are different for each language.
    An option could be having it extend the different languages, e.g. "MySerlizier : JavaSerlizier, TypeScriptSerlizier"

    \item \textbf{Template engine} Scriban, Cottle, Fluid \hyperlink{https://r3c.github.io/cottle/benchmark.html}{Cottle benchmark}
    
    \item \textbf{Keep it simple} Pas på med ekstra features. F.eks. property type. Det er fint til produktet, men giver intent akademisk

    \item \textbf{Roslyn} Compile time code anylse ting ting.
https://github.com/Digizuite/digizuite.core/tree/feature/sdk-generation/SourceGenerators/SdkLowLevelGenerator

    \item \textbf{Java implementation} Compile time code anylse ting ting.
        \begin{itemize}
            \item \textbf{Maven} - Automatic getter / setter / constructor
            \item \textbf{Lombok} - Automatic getter / setter / constructor
            \item \textbf{Retrofit} - Automatic HTTP client
        \end{itemize}

   \item \textbf{Standard}
\begin{verbatim}
    endpoints [{
        url: "localhost:/api/users/{userId}",
        placeholders [{
            name: "userId",
            type: "number"
        }],
        parameters: [{
            name: "deprecated",
            type: "boolean"
        }],
        body: {
        
        }
    }]
\end{verbatim}

    \item \textbf{Planning} \hyperlink{https://tree.nathanfriend.io/}{Website}
    \begin{verbatim}
Master Theisis (code part) [27.5 days]
  Generate DTOs [21]
    Default projects [1.5 day]
      Versioning - 0.5 days]
      Package Manager - 0.5 days
      Packages - 0.5 days
    Runtime vs compile time [6.5 days]
      Reflection [1.5 days]
        Understanding - 0.5 days
        Testing - 1 day
      Ryslin [5 days]
        Understanding - 2 days
        Testing - 2 days
        AST - 1 day
    Template Engine [3 days]
      - Research [2 days]
      - Testing [1 day]
    Creating the converter [8 days] [Blockeb by: Template Engine, Runtime vs compile time, default projects]
      Basic model [4 days]
        Mapping: 2 days
        Convert to Java: 1 day
        Convert to TS: 1 day
      Inheritance - [2 days]
        Mapping: 1 day
        Java: 0.5. days
        TS: 0.5 day
      Generics - [2 days]
        Mapping: 1 day
        Java: 0.5 days
        TS: 0.5 day
    Configuration [2 days]
      JSON parsers [0.5 days]
      Versions [0.5 days]
      Property names [1 day]
        Default [0.5 days]
        Custom [0.5 days]
          System.Text.Json
          Newtonsoft
      Custom serilizer [1 day]
      
  Version Validation [2.5 days]  [Blockeb by: Creating the converter]
    Defining rules [0.5 day]
    Implementing rules [2 days]
  Generate interfaces [4 days] [Blockeb by: Creating converter]
    Creating template [1 day]
      Java [0.5 days]
      TS [0.5 days]
    Creating model [2 days]
    Testing [1 day]
  Implementing interfaces [Wont do]
    Authentication
    Rate limit
    Errors
    \end{verbatim}
    

\begin{csharp}
// Variable
public string MyVariable = "Hello World!";

// Fuction
public string MyMethod(sting arg)
{
  // body
}
\end{csharp}

\begin{java}
// Variable
public String myVariable = "Hello World!";

// Fuction
public String myMethod(sting arg)
{
  // body
}
\end{java}

\begin{typescript}
// Variable
myVariable: string = "Hello World!";

// Fuction
function myMethod(arg: string): string
{
  // body
}
\end{typescript}


\end{itemize}


